Lyman-alpha spectra from rotating outflows

### 2017-10-19 paper/paper.tex
plots for line characterization
doppler line stats in paper

% Esta figura deberia tener 3 x 2 viñetas. tau=10E5.
% cada panel tiene una curva para no rotation, rotation (radiative transfer)
% y rotation (doppler)
% |vrot=50, vout=5,  | vrot=100, vout=5,  |
% |vrot=50, vout=25, | vrot=100, vout=25, |
% |vrot=50, vout=50, | vrot=100, vout=50, |
\begin{figure*}
  \begin{center}
    \includegraphics[width=0.90\textwidth]{./figures/results/doppler_shift}
  \end{center}
  \caption{\textbf{Caption:} Caption.
    \label{fig:doppler_shift}}
\end{figure*}

>>>>

% Esta figura deberia tener 3 x 2 viñetas. tau=10E6.
% cada panel tiene una curva para no rotation, rotation (radiative transfer)
% y rotation (doppler)
% |vrot=50, vout=5,  | vrot=100, vout=5,  |
% |vrot=50, vout=25, | vrot=100, vout=25, |
% |vrot=50, vout=50, | vrot=100, vout=50, |
\begin{figure*}
  \begin{center}
    \includegraphics[width=0.90\textwidth]{./figures/results/doppler_shift_6}
  \end{center}
  \caption{\textbf{Caption:} Caption. Tau 10E6.
    \label{fig:doppler_shift}}
\end{figure*}

In order to compare the line creative with the radiative transfer process that 
involves the rotation (RT) and the line with only outflows that is Doppler 
shifted (DS), we calculate three main characteristics for each spectrum. We 
measure the line's mean velocity, standard deviation and skewness for both 
RT and DS approaches. We plot the results for each value in Figures 
\ref{fig:mean_line}, \ref{fig:standard_deviation} and \ref{fig:skewness}, 
respectively for the same \tauh as Figure \ref{fig:doppler_shift}.

\begin{figure*}
	\begin{center}
		\includegraphics[width=0.90\textwidth]{./figures/results/mean_line_6}
	\end{center}
	\caption{\textbf{Caption:} The dots represent the Radiative Transfer and
		the lines represent the Doppler Shift. Tau 10E6.
		\label{fig:mean_line}}
\end{figure*}

\begin{figure*}
	\begin{center}
		\includegraphics[width=0.90\textwidth]{./figures/results/standard_deviation_6}
	\end{center}
	\caption{\textbf{Caption:} The dots represent the Radiative Transfer and 
		the lines represent the Doppler Shift. Tau 10E6.
		\label{fig:standard_deviation}}
\end{figure*}

\begin{figure*}
	\begin{center}
		\includegraphics[width=0.90\textwidth]{./figures/results/skewness_6}
	\end{center}
	\caption{\textbf{Caption:} The dots represent the Radiative Transfer and 
		the lines represent the Doppler Shift. Tau 10E6.
		\label{fig:skewness}}
\end{figure*}

This shows that the DS model can reproduce the main characteristics of the 
RT one. Because of this, we can introduce rotation effects in any spectra 
without running the radiative transfer simulations, that usually take a 
significant amount of time and computational resources.
